---
title: "R Notebook"
output: html_notebook
---

This is Problem Set 2 for Biostats Fall of 2022. I am establishing data analysis of Halloween Data.


As usual we clear everything and add our packages
```{r}
rm (list = ls())
library(dplyr)
library(ggplot2)
library(here)
```

Importing Data
#Adding stringsAsFactors = TRUE to change strings to factors and glimpse to double check
```{r}
DF <- read.csv(here("Data", "Halloween_data_PS2.csv"), stringsAsFactors = TRUE)
glimpse(DF)
```

Just looking at the Data Summary, Column Names, and Data Structure
```{r}
str(DF)
summary(DF)
colnames(DF)
```

#Fixing up some of the Data by turning everything lowercase and then stripped the white space using the mutate function
```{r}
DF <- DF %>%
  mutate(Costume = tolower(Costume), Type = tolower(Type))
DF <- DF %>% 
  mutate(Costume = trimws(Costume), Type = trimws(Type))
View(DF)
```

Here we delete the Data Rows 4, 12, 29, and 30, because of a lack of data from their dataset
```{r}
DF <- DF[-c(4,12,29,30),]
View(DF)
```

#Finding mean of age of trick-or-treaters and the mean number of pieces of candy taken broken down by Costume and Type for figure one
```{r}
Plot.DF <- DF %>% group_by(Costume, Type) %>% summarize(mean_age = mean(age), mean_candy = mean(candy_pieces))

print(Plot.DF)
```


Figure 1. Mean number of pieces of candy taken as a function of age of trick-or-treater and costume type 

```{r}
ggplot( Plot.DF, aes(x = mean_age, y = mean_candy, colour = Type)) +
  geom_point()+
xlab("Mean age of kids (years)")+
ylab("Mean number of pieces taken")+
theme_bw()
```


#code that isolates the data for children in “not scary” costumes who are 10 years old or younger and use the resulting data to plot a histogram showing the number of kids in each age class

```{r}
Plot.DF2 <- DF %>% filter(Type == "not scary" & age <= 10) 
```

Figure 2. Number of children age 10 and under wearing costumes that are not scary. 

```{r}
ggplot(Plot.DF2, aes(x = age))+
geom_histogram(bins = 4)
```

Figure 3. Box and whisker plot showing the age distribution of children wearing different Halloween costume choices, separated according to whether the costume is scary or not

```{r}
ggplot(DF, aes(x = Costume, y = age))+
  geom_boxplot()+ 
  facet_wrap(~Type)+
  coord_flip()
```

