---
title: "R Notebook"
output: html_notebook
---

This is Problem Set 2 for Biostats Fall of 2022


As usual we clear everything and add our packages
```{r}
rm (list = ls())
library(dplyr)
library(ggplot2)
library(here)
```

## Importing Data using here package
```{r}
DF <- read.csv(here("Data", "Halloween_data_PS2.csv"), stringsAsFactors = TRUE)
glimpse(DF)
```

#Structure, Summary, and Col Names of Data
```{r}
str(DF)
summary(DF)
colnames(DF)
```

#Fixing up some of the Data by turning everything lowercase and then stripped the white space
```{r}
DF <- DF %>%
  mutate(Costume = tolower(Costume), Type = tolower(Type))
DF <- DF %>% 
  mutate(Costume = trimws(Costume), Type = trimws(Type))
View(DF)
```

#Deleting rows of Data without data
```{r}
DF <- DF[-c(4,12,29,30),]
View(DF)
```

#Finding mean of age of trick-or-treaters and the mean number of pieces of candy taken broken down by Costume and Type
```{r}
DF %>% group_by(Costume, Type) %>% summarize(mean_age = mean(age), mean_candy = mean(candy_pieces))
```

```{r}

```

